---
output: rmarkdown::github_document
---

`cloudcidrs` : Tools to Obtain and Work with Cloud Provider CIDR Blocks

I'm only adding in cloud providers on a request basis (i.e. I only need the list that I
originally made, so if you need another cloud provider, file an issue or — prefereably — PR).

Most proviers do not provide an API or even an official list, so there's some elbow 
grease involved in a few of the functions to get as comprehensive of a list as possible for
each provider.

A future plan is to [`memoise`](https://cran.r-project.org/package=memoise) the results 
and also provide disk-level caching since these CIDRs don't change frequently enough to 
warrant network traffic for each call.

The following functions are implemented:

- `amazon_ranges`:	Amazon AWS cloud ranges
- `azure_ranges`:	Azure ranges
- `digitalocean_ranges`:	Digital Ocean ranges
- `google_ranges`:	Google Cloud ranges
- `rackspace_ranges`:	Rackspace ranges
- `softlayer_ranges`:	Softlayer ranges
- `normalize_ipv4`:	Normalize Cloud CIDR return values

### Installation

```{r eval=FALSE}
devtools::install_git("https://gitlab.com/hrbrmstr/cloudcidrs.git")
```

```{r message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r message=FALSE, warning=FALSE, error=FALSE, cache=TRUE}
library(cloudcidrs)

# current verison
packageVersion("cloudcidrs")

amazon_ranges() %>%  normalize_ipv4()

azure_ranges() %>%  normalize_ipv4()

digitalocean_ranges() %>%  normalize_ipv4()

google_ranges() %>%  normalize_ipv4()

rackspace_ranges() %>%  normalize_ipv4()

softlayer_ranges() %>%  normalize_ipv4()
```

### Test Results

```{r message=FALSE, warning=FALSE, error=FALSE}
library(cloudcidrs)
library(testthat)

date()

test_dir("tests/")
```

